---
title: "Introduction to lease"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to lease}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `lease` package provides a way to manage temporary connections to databases, specifically designed for single-user databases like DuckDB where file locks can be an issue.

## Basic Usage

A `lease` object acts as a proxy for a `DBI` connection. It automatically opens the connection when needed, keeps it open for a specified timeout, and retries with exponential back-off if the database is locked.

```{r setup}
library(lease)
library(DBI)
```

### Creating a Lease

You can create a lease using `dbLease()`. You provide a DBI driver and any arguments needed for `dbConnect()`.

```{r example}
# Create a lease for an in-memory DuckDB database
# (Using a file-based one would be more typical for lease)
db_lease <- dbLease(
  duckdb::duckdb(dbdir = ":memory:"), 
  timeout = 60,
  max_retries = 10
)
```

### Using the Lease

The `lease` package wraps many standard `DBI` methods. This means you can use the `db_lease` object directly where you would normally use a `conn`.

```{r dbi-methods}
# Write data
dbWriteTable(db_lease, "mtcars", mtcars)

# Query data
res <- dbGetQuery(db_lease, "SELECT * FROM mtcars LIMIT 5")
head(res)

# List tables
dbListTables(db_lease)
```

